Using an SMT engine to generate Symbolic Automata

### 2019-03-06 2017-Xudong-SMT/ActaInformatica.tex
more todos, and added proof of Th1

@@

@@

In a pLTS, there may be several incoming transitions 
that assign potentially different values to a state variable.
To handle such cases, the algorithm manages, for each pLTS state, a
list of expressions collected from the assignments of each state
variable. %% $v$.
%% The list we used contains triples <$v$, $S$, $AssignRH$> 
%% where $v$ is the variable in pLTS, $S$ is its owner state and
%% $AssignRH$ is a list of expressions over other variables in the right
%% hand side of assignments of $v$.
% As a pragmatic extension to the formal definition, we also manage
% ``global variables'', defined in all states of the pLTS.
For a global state in the open automaton, the set of state
variables (which may be used in a transition) %% will simply be
is the disjoint union
of sets of state variables of the individual pLTS states constituting this
global state.
%There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables). There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results. In order to avoid such mistakes,

@@

The safety
property \emph{``There is always a possibility to reset the system
  after a single failure''} (\ie without
  additional failures having to occur in the meantime) enforced by the
  Failure Monitor architecture can be specified using CTL as
    $\AG
\bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
  \PortReset}\bigr)$.  Additional properties are provided in \ref{RR}.

@@

Figure \ref{fig:ArchFailure:OA} shows the open automaton built by our
algorithm. For reasons of readability, we did not show the full
details of the open transitions on this figure. Below we list the
first 3 of them (full details available in \ref{RR}). 
This automaton has 12 transitions, including those encoding various
possible firing of some interactions (e.g. OT 2 and 3 for
{\PortFail}). It looks like the rough behaviour is
reasonable, although a detailed study shows that the property stated
above does not hold, because of the
{\PortFail} loops on states $11$ and $12$. This is because we did not
use the maximal progress assumption here. If we do, we get the
corrected behaviour in Figure \ref{fig:ArchFailure:OA-MaxProgress}, in
which $OT_7$ has disappeared, and $OT_2$ and 
$OT_{10}$ have been restricted to $b0=\false$.

>>>>

\TODO{the proof of the finiteness theorem refers to SOS rules Tr1 and
  Tr2. So maybe we must include (and explain) these here. One problem
  is that these rules have been modified/improved with each new
  publication of pNets papers, so we have to decide which version we
  use here}

@@

\begin{proof}
  \noteEM{I tentatively copied the proof here, from RR-8898. We should
    check if it is sufficient with this version of the algorithm, or
    if it can be make more precise (some added analysis of the
    behavior of matching/combining/filetring ?)}
  The possible set of states of the open-automaton is the cartesian
  product of the states of its leaves $pLTS_i^{i\in L}$, that is finite by
  hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
  iteration terminates. The enumeration of open-transitions in step 2b is bounded by the
  number of applications of rules Tr2 on the structure of the
  pNet tree, with a finite number of synchronisation vectors applying
  at each node the number of global open transition is finite. Similarily rule Tr1 is 
  applied finitely if the number
  of transitions of each pLTS is finite. So we get finitely many deduction trees, and
  open-transitions which ensures that each internal loop of Algorithm 1 terminates.
  \end{proof}

@@

In a pLTS, there may be several incoming transitions 
that assign potentially different values to a state variable.
To handle such cases, the algorithm manages, for each pLTS state, a
list of expressions collected from the assignments of each state
variable. %% $v$.
%% The list we used contains triples <$v$, $S$, $AssignRH$> 
%% where $v$ is the variable in pLTS, $S$ is its owner state and
%% $AssignRH$ is a list of expressions over other variables in the right
%% hand side of assignments of $v$.
% As a pragmatic extension to the formal definition, we also manage
% ``global variables'', defined in all states of the pLTS.
For a global state in the open automaton, the set of state
variables (which may be used in a transition) %% will simply be
is the disjoint union
of sets of state variables of the individual pLTS states constituting this
global state.
%There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables). There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results. In order to avoid such mistakes, 
\TODO{these assignment sets collect potential assignments from all OTs
  in the generated automaton. If we minimize the generated state
  space, we will get less assignements, and potentialy also get better
  minimization... }

@@

The safety
property \emph{``There is always a possibility to reset the system
  after a single failure''} (\ie without
  additional failures having to occur in the meantime) enforced by the
  Failure Monitor architecture can be specified using CTL as
    $\AG
\bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
  \PortReset}\bigr)$.  Additional properties are provided in \ref{TimerRR}.

@@

Figure \ref{fig:ArchFailure:OA} shows the open automaton built by our
algorithm. For reasons of readability, we did not show the full
details of the open transitions on this figure. Below we list the
first 3 of them (full details available in \ref{TimerRR}). 
This automaton has 12 transitions, including those encoding various
possible firing of some interactions (e.g. OT 2 and 3 for
{\PortFail}). It looks like the rough behaviour is
reasonable, although a detailed study shows that the property stated
above does not hold, because of the
{\PortFail} loops on states $11$ and $12$. This is because we did not
use the maximal progress assumption here. If we do, we get the
corrected behaviour in Figure \ref{fig:ArchFailure:OA-MaxProgress}, in
which $OT_7$ has disappeared, and $OT_2$ and 
$OT_{10}$ have been restricted to $b0=\false$.
